---
title: "COVID-19 is Coming Back"
author: "Xiangyu Wang"
date: 2020-09-24
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
bibliography: 'references.bib'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("opendatatoronto")
install.packages("tidyverse")
library(opendatatoronto)
library(tidyverse)
library(dplyr)
```

```{r}
toronto_covid_packages <- search_packages("COVID")
toronto_covid_resources <- toronto_covid_packages %>% list_package_resources()
toronto_covid_statistics <- toronto_covid_resources %>% get_resource()

```
#Part.i Abstract

  I used bar plots to visualize the Toronto COVID-19 data offered by Toronto Public Health. The observation were adult between age 19 and 69 was a primarily infected group by the COVID-19, and the case report shows clear evidence that COVID-19 cases, again, are rising fast. As data suggests, we need to prepare another incoming outbreak.
  Tools and data used @citetidyverse

#Part.ii Introduction 

  I want to call the year 2020 as a drama, and COVID-19 plays as the protagonist. To view it globally, it affects many things from politics to economics; to view it near, it changes the way we work, study, and many other things imaginable. 
  So, as the weather gets colder, we need to prepare for the future impact of COVID-19. And this study will show specific infection data of COVID-19 to help you understand that it is more lithal to elders than young people, and it is most likely coming back in the upcoming cold days. 

#Part.iii Data Discussion

   Toronto Public Health offers this data set, and it is the version updated by September 23, 2020. It contains 18 variables with 17872 reported COVID-19 infection cases. The variable features I used will be explained next below to its corresponding plot or code section.
   
```{r}
glimpse(toronto_covid_statistics)
```

```{r}
current_stats_1 <- colSums(toronto_covid_statistics == 'Yes')
current_stats_1[current_stats_1 > 0]
```
  The code above demonstrates the current and ever hospitalized, ICU, and Intubated cases related to the infection of COVID-19. The 'Currently' cases are included in 'Ever' cases.
  The hospitalized rate is 0.11 (11%) and can be calculated by 1990 (ever hospitalized case)/ 17872 Cases (including probable cases). So it seems like most people infected by COVID-19 do not need to be hospitalized. But is that so? Let's look into data more deeply.

#Part.iv Plots

```{r}
ggplot(data = toronto_covid_statistics) +  aes (x = toronto_covid_statistics$`Age Group`) + geom_bar(color = "black",fill = "skyblue2") + labs(x = 'Age Group', y = 'Case Count', title = 'Toronto COVID-19 Cases in All Age Groups')
```
  The plot above shows the age groups that infected by COVID-19. On the x-axis, the age group divides by multiple sessions; each session has a year range of 10.
  We can observe that adults between ages 19 and 69 were primarily infected groups by the COVID-19; this may be caused by daily activities like working, shopping, etc. We will come to the infection source later on in the study.
  Note: The NaN part in the plot is mainly caused by data missing on the cases' age.

```{r}
hospitalized_data <- filter(toronto_covid_statistics, toronto_covid_statistics$`Ever Hospitalized` == 'Yes')
ggplot(data = hospitalized_data) +  aes (x = hospitalized_data$`Age Group`) + geom_bar(color = "black",fill = "skyblue2") + labs(x = 'Age Group', y = 'Case Count', title = 'All (Current and Ever) Hospitalized Cases in All Age Groups')
```
  When we look closely at hospitalized data, we found that elders are more likely to be hospitalized than young people. So 'most people infected by COVID-19 do not need to be hospitalized' is a false statement. So please be responsible for your actions and take good care of elders around you! They are more vulnerable than you when you are both exposed to the virus.

```{r}
Intubated_data <- filter(toronto_covid_statistics, toronto_covid_statistics$`Ever Intubated` == 'Yes')

ggplot(data = Intubated_data) +  aes (x = Intubated_data$`Age Group`) + geom_bar(color = "black",fill = "skyblue2") + labs(x = 'Age Group', y = 'Case Count', title = 'All (Current and Ever) Intubated Cases in All Age Groups')
```
  The intubated data again shows the elder is extremely vulnerable when infected, most groups with age above 50 even have an intubated rate of more than 20%ï¼ (20% was calculated roughly by 80 divide 350).

```{r}
ggplot(data = toronto_covid_statistics) +  aes (x = toronto_covid_statistics$`Client Gender`) + geom_bar(color = "black",fill = "skyblue2")  + labs(x = 'Case Gender', y = 'Case Count', title = 'COVID-19 Cases with Different Gender') 
```
  The above plot shows COVID-19 cases with different gender, and there are more female cases than male cases. A possible assumption is that female is more vulnerable than male. But it contains much possible bias such as male may treat COVID-19 as merely as getting cold and then do not report the case. But it is not the learning goal of my study this time. We may talk about this in future studies.
  
```{r}
ggplot(data = toronto_covid_statistics) +  aes (x = toronto_covid_statistics$`Source of Infection`) + geom_bar(color = "black",fill = "skyblue2")  + labs(x = 'Infection Source', y = 'Case Count', title = 'Source of Infection of Toronto COVID-19 Cases') 
```

  

```{r}
ggplot(data = toronto_covid_statistics) +  aes (x = toronto_covid_statistics$`Episode Date`) + geom_bar(color = "black",fill = "skyblue2")  + labs(x = 'Episode Date Since 2020', y = 'Case Count', title = 'Toronto COVID-19 Cases by Episode Date') 
```


# Plots Discussion


# Reference




